### 2014-03-07 src/conclusion.Rnw
udpate

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
@
\end{comment}

% <<a,message=F, echo=F>>=
% require(xtable)
% require(data.table)
% load('data/mu.rda')
% @

% 10 pages for the main text + 1 for references.
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
<<intro, child='intro.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
<<methodology, child='methodology.Rnw'>>=
@
<<analysis, child='analysis.Rnw'>>=
@

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

o <- subset(oprand, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(oprand, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
@

<<results='asis'>>=
opsel <- subset(stats.df,grepl('^..op', rownames(stats.df)))

o <- subset(opsel, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:selo'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(opsel, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:selr'), include.rownames=FALSE)
@

\subsection{Correlation Analysis}

$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $

The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.

\subsubsection{sdl.mut.avg and mut.avg}

% <<>>=
% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
% @

$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$

\subsubsection{lrnd.mut.avg and mut.avg}

$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$

\subsection{Regression Analysis}
The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling. We can perform two statistical tests to answer this question. For the first, we run a simple paired t-test.

%<<>>=
%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
%@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
Our full model is

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
% <<results='asis'>>=
% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
% s$type <- 'sdl'
% colnames(s) <- c('mut', 'sample', 'type')
% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
% r$type <- 'rnd'
% colnames(r) <- c('mut', 'sample', 'type')
% all <- rbind(s, r)
% fm <- with(all, lm(mut ~ sample + type + sample:type))
% sm <- anova(fm)
% print(xtable(sm,caption="My caption"), size="\\small")
% @
\end{small}

We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness. Hence, the techniques random sampling and statement deletion operator do not have any difference.

\begin{figure*}[t]
% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% t_f <- sdl.time~lrnd.time
% plot(t_f, main='SDL ~ RND',pch='*')
% abline(lm(t_f), col='red')
% detach(m)
% @
\caption{Time}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/original.pdf}
\caption{Subsumption Original}
\label{fig:subsumptiono}
\end{figure*}[t]

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]

<<results, child='results.Rnw'>>=
@

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}
\section{Results}

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.

The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}

>>>>

\section{Conclusion}
\label{sec:conclusion}

### 2014-03-07 src/intro.Rnw
udpate

% 1. Describe the problem
% 2. State your contributions

TODO: Mutation analysis is a transformation of programs that generates several mutants 
Mutation analysis originally proposed by Lipton\cite{lipton1971fault} involves systematic transformation of program through introduction of first order syntactical changes\cite{ammann2008introduction}. Researchers have shown that the mutations thus introduced behave similarly to the real faults\cite{andrews2005mutation}, and hence can be used as a stand-in for real faults when determining the efficacy of a test suite against faults.

Programs can be modified in many different ways to generate mutants, thus, the set of 
possible mutants of programs can be very large introducing a high computational cost.
The computational cost has hindered wider use of mutation analysis.

Several studies has tried to devise techniques to reduce the cost of mutational analysis.
\begin{comment}
  Offut \cite{offutt2001mutation} classifies these techniques into the following three categories:
  \begin{enumerata}
  \item \emph{Do fewer}: techniques that try to reduce the number of mutants.
  \item \emph{Do faser}: techniques that 
  \item \emph{Do smarter}: techniques that 
  \end{enumerate}
\end{comment}
One of the main approaches is selective mutation which reduces the set of mutagens\footnote{We use the terms mutagens 
and mutation operators interchangably hereafter.}.
Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators. 
Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the 
mutagens and observed negligible loss of effectiveness in mutation analysis. 
Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
that using only statement deletion operator gives a close approximation of original mutation score.

While some studies try to 
find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others 
have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.

\begin{comment}
  These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.

  % TODO check the survey again on selective mutation.

  It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.

  Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.

  However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.

  In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
\end{comment}

In this paper, we study the effects of different mutation selection and sampling on the effictiveness of 
mutation analysis and the computational costs. We have used more than 107 real world projects for our
experiments.

This paper follows in this order: Section \ref{sec:methodology} describes the methodology.
Section \ref{sec:implementation} explain our experiment setting and implemetation.
Results of experiments are summarized in Section{sec:results}. Section \ref{sec:anaysis}
provides analysis of the results. Section \ref{sec:related} provides the related work. 
Finally, Section \ref{sec:conclusion} concludes the paper.

>>>>

% 1. Describe the problem
% 2. State your contributions
Mutation analysis is a method of evaluation of quality of test-suites. It involves generation
of first (and higher) order mutants, and evaluating the effectiveness of test-suites against
the generated mutants~\cite{lipton1971fault, ammann2008introduction}.
Previous research~\cite{andrews2005mutation} has shown that mutations thus introduced behave
similar to the real-faults.

A major impediment on the path to wide adoption of mutation analysis is its high cost of
execution. A full mutation analysis requires running the test-suite against all the first
order syntactical variants, and is prohibitive for even moderately large programs.

A major strain of research into cost-reduction of mutation analysis is to choose a smaller
representative set of mutants~\cite{offutt2001mutation,jia2011analysis}, often called the
``do fewer'' approach. A major variant of this approach is the selective mutation strategy
which advocates selecting a representative subset of operators based on heuristics and
statistical analysis, and using them instead of the whole gamut of mutation
operators~\cite{offutt1993anexperimental,untch2009onreduced}.

Another fertile area of research has been sampling strategies, where, a smaller representative
sample is used in lieu.
This was investigated first by Acreed~\cite{acree1980mutation} and Budd~\cite{budd1980mutation},
who proposed using only $x$\% of the mutants produced. The studies by Wong and
Mathur, found that random sampling with ratio as low as 10\% could provide
accurate results~\cite{jia2011analysis}.

%Mathur \cite{} reduced the number of mutagens in Mothra \cite{Mothra} by omitting two operators.
%Offutt et al.\cite{offutt1993anexperimental} further omitted upto six oprators from the
%mutagens and observed negligible loss of effectiveness in mutation analysis.
%Unch\cite{untch2009onreduced} and more recently Deng et al.\cite{deng2013empirical} suggest
%that using only statement deletion operator gives a close approximation of original mutation score.

%While some studies try to
%find the \emph{sufficient} subset of mutagens, like\cite{siami2008sufficient}, others
%have suggested that \emph{random} selection of mutants works as fine, e.g. \cite{zhang2010operator}.
%Some approaches combine the selective mutation selection and random selection, e.g. \cite{zhang2013ase}.

Finally, clustering of mutants~\cite{hussain08mutation} based on similar test cases has also
been used successfully for mutant reduction. These are explained more in depth in Section~\ref{sec:related}

While all these areas of research has been relatively successful in reducing the number of mutants
produced, there has been comparitively few studies that compares the approaches taken. The studies
that has been attempted so far, has been limited by the comparitively small number of sampled projects.

Our contributions in this paper are the following. First, as described in Section~\ref{sec:methodology},
we seek to improve the statistical confidence in our results by utilizing a much larger sample of projects
(188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
generated test-suites using Randoop~\cite{randoop}. Second, as detailed in Section~\ref{sec:analysis}, we
compare the reduction effectiveness of a large number of random sampling criterias (some of which are novel,
and some that has been proposed by other researchers), and a some of the common operator selection
criterias proposed in literature using statistical analysis. This provides us with insight for choosing
mutation reduction techniqus according to the trade-offs in accuracy, and reduction ratios that a tester
is willing to make for their specific requirements. This is detailed in Section~\ref{sec:results}.

Our conclusion and recommendation for practicing testers are provided in Section~\ref{sec:conclusion}.

% \begin{comment}
%   These approach relies on the fact that some of the mutagens generate a large number of variants, and hence produce highly redundant test cases. Previous research suggested that elimination of mutagens with high fertility results in the reduction of total number of mutations produced, and hence reduces the computational requirements.
%
%   % TODO check the survey again on selective mutation.
%
%   It was recently questioned whether this approach indeed resulted in a tangible improvement over random selection of mutants\cite{zhang2010operator}, which did not find operator based selection to be better than random selection.
%
%
%   Another research, initially by Unch\cite{untch2009onreduced} and recently by Deng et al.\cite{deng2013empirical} suggests using software deletion operator since it produces the least number of mutants (smallest neighborhood). The researchers were able to obtain a close approximation of original mutant score with significant savings with this approach.
%
%   However, our previous research suggests that mutation coverage is closely predicted by statement coverage, this suggests that any criteria that forces accounting of the impact of each statement should provide a close approximation to the full mutation score. Hence, our research suggests that SDL works because it forces accounting of each line, and a random sampling criteria that provides the same criteria should result in similar results.
%
%   In our analysis, we find that a random sampling approach that randomly chose a single mutant per line was found to have a better correlation with the full mutation score than that obtained by SDL. Further it was also found that the mutation score produced by random sampling was closer to the full mutation score than that produced by SDL.
%
% Order of most fertile operators for N-selective operator selection.
% NON_VOID_METHOD_CALLS
% NEGATE_CONDITIONALS
% REMOVE_CONDITIONALS
% DELETE_CONDITIONALS
% RETURN_VALS
% INLINE_CONSTS
% CONSTRUCTOR_CALLS
% EXPERIMENTAL_MEMBER_VARIABLE
% VOID_METHOD_CALLS
% MATH
% CONDITIONALS_BOUNDARY
% INCREMENTS
% REMOVE_INCREMENTS
% RMSWITCH
% EXPERIMENTAL_SWITCH
% INVERT_NEGS
%
% \end{comment}
%
%

### 2014-03-07 src/paper.Rnw
udpate

<<results, child='results.Rnw'>>=
@

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}
\section{Results}

We see from the data that random sampling has a higher $R^2$, and also approximates the all  mutations score better.
However, caveat emptor. There is a difference between the number of mutators for SDL and RAND. If our approximation was right, we should have gotten nearly same number of mutators. However
The number of mutators in RND is
 Sexpr{sum(m.lrnd.pit.mutation.total) / sum(m.sdl.pit.mutation.total)} times SDL.

The total mutants for all is Sexpr{sum(m.pit.mutation.total)}, for rnd is Sexpr{sum(m.lrnd.pit.mutation.total)} and for sdl is Sexpr{sum(m.sdl.pit.mutation.total)}

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}

>>>>

<<results, child='results.Rnw'>>=
@
<<results, child='conclusion.Rnw'>>=
@
